### 2014-04-29 ApTranscriptome_TR.Rmd
Updates to script - cleaning up file for knitting

**April 10, 2014**

@@

```{r download, echo = TRUE, results = "hide"}
### Annotation file
# from either AWS or GoogleDrive
annotationURL <- getURL("http://johnstantongeddes.org/assets/files/Aphaeno_transcriptome_AnnotationTable.txt")
#a2 <- getURL("https://googledrive.com/host/0B75IymziRJ_9Tlg1U1Vxbjk1bzg") # GoogleDrive link

@@

# merge results
Ap.response.type <- rbind(interaction.response.type, temperature.response.type)
colnames(Ap.response.type)[which(colnames(Ap.response.type) == ".id")] <- "Transcript"
str(Ap.response.type)
```

@@

pdf(paste(resultsdir, "Ap.BP_topGO_sig_nodes.pdf", sep=""))
showSigOfNodes(Ap.BP.GOdata, score(Ap.BP.resultParentChild), firstSigNodes = 10, useInfo = 'all')
dev.off()
```

@@

# Run GSEA
Ap.high.gsea <- gsea(genelist = Ap.geneList.high, geneID2GO = geneID2GO, plotpath = "results/Ar_int_BP_topGO_sig_nodes.pdf")
#pandoc.table(Ap.high.gsea)
# output for Revigo
write.table(Ap.high.gsea[,"GO.ID"], file = "results/Ap_high_gsea.txt", row.names = FALSE, sep = "\t", quote = FALSE)
```

>>>>

**April 29, 2014**

@@

```{r download, echo = TRUE}
### Annotation file

# from either AWS or GoogleDrive
annotationURL <- getURL("http://johnstantongeddes.org/assets/files/ApTranscriptome_AnnotationTable_20140113.txt")
#a2 <- getURL("https://googledrive.com/host/0B75IymziRJ_9Tlg1U1Vxbjk1bzg") # GoogleDrive link

@@

# merge results
Ap.response.type <- rbind(interaction.response.type, temperature.response.type)
colnames(Ap.response.type)[which(colnames(Ap.response.type) == ".id")] <- "Transcript"
str(Ap.response.type)

# save results to file
write.table(file = paste(resultsdir, "Ap_responsive_transcripts.txt", sep = ""), Ap.response.type, row.names = FALSE, col.names = TRUE, quote = FALSE, sep = "\t")
```

```

@@

#pdf(paste(resultsdir, "Ap.BP_topGO_sig_nodes.pdf", sep=""))
#showSigOfNodes(Ap.BP.GOdata, score(Ap.BP.resultParentChild), firstSigNodes = 10, useInfo = 'all')
#dev.off()
```

@@

# Run GSEA
Ap.high.gsea <- gsea(genelist = Ap.geneList.high, geneID2GO = geneID2GO, plotpath = NA)
#pandoc.table(Ap.high.gsea)
# output for Revigo
write.table(Ap.high.gsea[,"GO.ID"], file = "results/Ap_high_gsea.txt", row.names = FALSE, sep = "\t", quote = FALSE)
```
